Does pre-crastination explain why some observers are sub-optimal in a visual search task?

### 2023-10-03 RegReport/paper_nomarkup.tex
no markup version

% \maketitle
\begin{abstract}
How do we decide where to search for a target? Optimal search relies on first considering the relative informational value of different locations, and then executing eye movements to the best options. But many participants consistently move their eyes to locations that can be easily ascertained to neither contain the target, nor to provide new information about the target's location. Here we \textcolor{red}{asked} whether this sub-optimal search behaviour represents a specific example of a general tendency towards \textit{pre-crastination}: starting sub-goals of a task before they are needed, and in so doing, spending longer doing the task than is necessary. To test this hypothesis, we \textcolor{red}{asked} 200 participants to do two tasks: retrieve two heavy buckets (one close and one far), and search for a line segment. Pre-crastination is defined as consistently picking up the closer bucket first, versus the more efficient strategy of picking up the farther bucket first. Search efficiency is the proportion of fixations directed to more cluttered regions of the search array. \textcolor{red}{Based on pilot data, we predicted} an association of pre-crastination with inefficient search strategies. Personality inventories \textcolor{red}{were} also administered to identify stable characteristics associated with these strategies. \textcolor{red}{In the final dataset, there was no clear association between search strategy and pre-crastination, nor did these correlate strongly with any of the personality measures collected.}
\end{abstract}

@@

\begin{figure}
\centering
\includegraphics[width=6cm]{Figures/split-half.png}
\caption{An example of the split-half line segment stimuli. The target is the unique line segment oriented $45^{\circ}$ to the right. Participants who direct their saccades to the heterogeneous half of the display are faster to correctly respond target absent/present than those who fixate the homogeneous half of the display.}
\label{fig:stimulus}

\end{figure}

@@

In the present study, we \textcolor{red}{investigated} the hypothesis that participants who are sub-optimal in our split-half line segment search task have a tendency towards \textit{pre-crastination}, a phenomenon where participants prioritise the completion of a sub-goal, even if it results in extra effort overall \cite{rosenbaum2014}. In the original study, participants were asked to walk down a corridor, pick up one of two heavy buckets as they passed, and carry it to the finish line. The two buckets were placed at different distances between the start and finish line, and the optimal (in terms of minimising effort) strategy is to pick up the bucket that is furthest from the starting position and closer to the finish line. Despite this simple solution, most participants favoured picking up the first bucket they came to, even though that resulted in them having to carry it further. This tendency was named \textit{pre-crastination}, and has since been replicated several times in both humans \cite{fournier2019task} and pigeons \cite{wasserman2015}. In an even more dramatic version of the task, Fournier and colleagues (2019) asked participants to go get two buckets - one close and one further away - and bring them back to set them on a table behind them. The majority (36 out of 49 participants in the key condition) chose to pick up the close bucket first, carry it out to the further bucket, and then bring both back, even though this order is clearly more effortful than picking up the far bucket and then grabbing the close one on the way back to the table.

As a first step to assessing our hypothesis, we conducted a pilot study to ensure we would replicate the variability between participants in a shorter version of the search task, and that we could clearly classify people into two groups based on whether they pick up the close bucket first (i.e. "pre-crastinators") or the farther bucket (optimal). The pilot data were also intended to be used to refine our approach to data processing, visualization, and analysis. Both of the previous findings (search variability, \cite{nowakowska2017}, and pre-crastination, \cite{fournier2019task}) were clearly replicated in the pilot experiment. Surprisingly, the data suggested a relatively robust relationship between pre-crastination and visual search strategy, but in the opposite direction to the one which we originally expected, with pre-crastinators having a tendency to search more efficiently rather than less. We therefore revised our aim to be more data-driven than the original hypothesis, aiming to estimate the variability in search performance accounted for by pre-crastination. The pilot data also suggested that the relationship between pre-crastination and visual search may by mediated by differences in speed-accuracy trade-offs between participants, so we \textcolor{red}{planned} to explore this aspect of visual search as well.

If we confirm the existence of a relationship between these two tasks, a natural question is whether this can be accounted for by personality traits of the individuals.  A personality trait is an enduring pattern of thoughts, feelings, and behaviours that is stable across time and contexts \cite{funder2016}. Previous research suggests that those who precrastinate are motivated, responsible, and energetic \cite{rosenbaum2019}. Specifically, \cite{sauerberger2019} found a correlation of $r = 0.22$ between precrastinaion and conscientiousness, which we \textcolor{red}{attempted} to replicate. Speculatively, these traits may also cause participants to search in a more thorough, but less efficient, manner, aligning with the interpretation that precrastinating, although costly, may not be irrational to the degree that participants prefer maximizing thoroughness over maximizing efficiency. Personality traits in this study \textcolor{red}{were examined} to help further uncover the individual difference factors associated with precrastination and different visual search strategies.

Our experiment \textcolor{red}{tested} the hypothesis that pre-crastination might represent a rational approach to doing tasks, i.e., a reasonable tendency to get the difficult part of the task out of the way first. If precrastination \textcolor{red}{had been} positively related to efficient search, this would be evidence in favour of a ``rational'' interpretation of precrastination, as opposed to the alternative interpretation that it reflects an irrational impulse to grab the closest task-related object (in which case, a negative correlation with search efficiency would \textcolor{red}{have been} more likely). In addition, the experiment \textcolor{red}{had} the potential to assess whether the already-established link between pre-crastination and conscientiousness could generalize, and be a potential explanation for the wide range of different search strategies previously observed. This would have important implications for theories of visual search, which tend to make assumptions about how ''people'' (as a group) direct their eyes during search; if personality traits can be directly predictive of eye movement strategies, this \textcolor{red}{would} challenge the field to more carefully refine its assumptions. In addition to the clear theoretical contribution our results could have \textcolor{red}{had}, they could also \textcolor{red}{have illustrated a case where} efficient/optimal tendencies in one circumstance can translate to inefficient choices in others. Finally, we have noticed in many fields that there is a lack of correlational studies relating behavioural measures to each other (as opposed to relating behavioural measures to personality traits).

@@

As such, we \textcolor{red}{investigated} the following hypotheses:

@@

\textcolor{red}{We planned to recruit} 200 participants for this experiment. This large sample size is due to the addition of personality measures: Larger samples provide greater power to detect the typical effect sizes in those fields, reduce Type I error, and increase the chances of replicable findings \cite{fraley2014}. Participants \textcolor{red}{were} recruited via participant panels and opportunity sampling at the universities of Aberdeen and Essex. The protocol \textcolor{red}{was} approved by the ethics committees at both universities. Participants \textcolor{red}{completed} the bucket-retrieval task both before and after the visual search task, so no counterbalancing \textcolor{red}{was} needed. Additional participants \textcolor{red}{were} recruited to replace \textcolor{red}{those} excluded from data analysis (details below).

@@

Figure \ref{fig:buckets} is a photograph of the bucket task set-up. Two 10 litre buckets \textcolor{red}{were} filled with sand until the total weight of each bucket \textcolor{red}{was} 3kg. The experiment \textcolor{red}{took} place in a quiet corridor. Buckets \textcolor{red}{were} placed at 6ft and 16ft away from the start position, which \textcolor{red}{was} marked as a T with green tape. Buckets \textcolor{red}{were} placed on crates at about hand height. Just behind the start position \textcolor{red}{was} a pair of crates on which to set the buckets down to end the trial.

@@

The task replicates that used in \cite{fournier2019task}, in which participants were instructed to pick up two buckets and place them on the crates behind the start position. We closely \textcolor{red}{followed} the methods and instructions as described in their appendix. Each participant \textcolor{red}{completed} three trials before the visual search task, and three trials after. While the experimenter \textcolor{red}{was} setting up the buckets for the next trial, the participant \textcolor{red}{was} asked to walk over to a nearby window and look outside until asked to return. The full protocol and instructions given to participants is available at https://osf.io/5aq4c/.

@@

Participants \textcolor{red}{were} classified as "pre-crastinators" if they \textcolor{red}{picked} up the closer bucket first, and "optimal" if they \textcolor{red}{picked} up the far bucket first. Based on the pilot data, and that of \cite{fournier2019task}, we \textcolor{red}{expected} the results from the bucket task to be largely binary, with participants picking up either the close or the far bucket on every trial. \textcolor{red}{Our plan was the following:} If the data are similarly binary in this experiment, we will continue to treat pre-crastination as a two-level categorical factor. Participants who pick up the closest bucket on at least five of the six trials will be classed as pre-crastinators, while those who pick up the closest bucket on no more than two out of six trials will be non-pre-crastinators. Participants with intermediate behaviour will be excluded.

There \textcolor{red}{was} also a chance that, unlike \cite{fournier2019task}, our sample of participants \textcolor{red}{would} give rise to a larger range of intermediate behaviours. If more than $25\%$ of our participants would \textcolor{red}{have been} excluded under the coding scheme outlined above, then we \textcolor{red}{would have treated} our pre-crastination measure as a three-level factor (if a clear classification is apparent). In this case, the same Bayesian beta regression model \textcolor{red}{would have been} fit to the data.

@@

Stimuli \textcolor{red}{were} presented on a 17 inch CRT monitor with a resolution of $1024 \times 768$. Stimulus generation, presentation and data collection \textcolor{red}{were} controlled by Matlab and psychophysics toolbox \cite{brainard1997,cornelissen2002} run on a mac pro computer. The position of the right eye \textcolor{red}{was} recorded using a desktop-mounted EyeLink 1000 eye tracker (SR Research, Canada) sampling eye position at 1000Hz.

We \textcolor{red}{used} the same arrays of line segments as in \cite{nowakowska2017} (see Figure \ref{fig:stimulus}). These arrays consist of 22 column and 16 rows on a uniform grey background. The target line is always tilted $45^{\circ}$ degrees to the right, while the mean distractor angle is perpendicular at $45^{\circ}$ degrees to the left. Search difficulty \textcolor{red}{was} manipulated by sampling from either a narrow $30^{\circ}$ range of distractor line orientations (homogeneous) or a wide $106^{\circ}$ range (heterogeneous). Half of each search array consists of homogeneous line segments, while the other half is heterogeneous. Which side is heterogeneous \textcolor{red}{was} randomly determined on each trial. We \textcolor{red}{used} 96 search trials in total, half of which \textcolor{red}{contained} a target. This number of trials was selected based on simulating the results of shorter experiments using the data from \cite{nowakowska2017} (see Figure \ref{fig:num_trials}). The target could be located in any of the possible locations apart from the middle four vertical columns.

@@

\subsubsection{Procedure} Before the start of the visual search experiment, participants undergo a nine-point calibration sequence. Following this, participants \textcolor{red}{were} instructed to report, as quickly as possible, whether a line tilted $45^{\circ}$ to the right was present or not, using the up (present) or down (absent) arrow key. Each search trial begins with a black fixation point (letter \texttt{x}) subtending $1.5\times 2.5$cm ($1.9^{\circ}\times 3.1^{\circ}$), presented at the centre of the computer screen. On the press of a space bar, the stimulus is displayed until the participant makes a response (or times out after 60 seconds). Auditory feedback in the form of a beep, and a 2s red screen, immediately follows incorrect key presses. A set of 8 practice trials precedes the experimental trials.

@@

Data from participants who fail to achieve at least $75\%$ accuracy for \textit{easy} and \textit{absent} conditions \textcolor{red}{were} excluded as it suggests that they did not understand the task. Fixations during trials \textcolor{red}{were} classified as falling on the homogeneous or heterogeneous half of the display, with fixations falling within the central four columns of line segments being excluded. Following \cite{nowakowska2017} we \textcolor{red}{summarised} each participant's strategy as the proportion of fixations two through five falling on the heterogeneous side of the display during target absent trials. Trials with fewer than five fixations \textcolor{red}{were} excluded, and we only \textcolor{red}{analysed} data from participants who have at least 10 trials.

@@

We \textcolor{red}{administered} three personality questionnaires. The first questionnaire is the second iteration of the Big Five Inventory (BFI-2 \cite{soto2017}). The BFI-2 measures five broad personality traits: extraversion (e.g., ``is outgoing, sociable''), agreeableness (e.g., ``has a forgiving nature''), conscientiousness (e.g., ``is efficient, gets things done''), negative emotionality (e.g., ``can be tense''), and open-mindedness (e.g., ``is fascinated by art, music, or literature''). Based on previous research, we \textcolor{red}{suspected} that precrastination will have the strongest relationship with conscientiousness. Those who are high in conscientiousness are organised, productive, and responsible, and may have an urge to pick up a bucket as soon as possible.

The second personality questionnaire is the Barratt Impulsiveness Scale (BIS-11 \cite{patton1995}). The BIS-11 measures overall impulsiveness, as well as three subtypes: attentional impulsiveness (``I don't `pay attention'''), motor impulsiveness (``I act on the spur of the moment''), and non-planning impulsiveness (``I say things without thinking''). Based on previous research, we \textcolor{red}{suspected} that neither impulsiveness nor its subscales will be related to precrastination.

@@

Personality questionnaires \textcolor{red}{were} administered to participants at the end of the experiment to prevent them from influencing the behavioural measures. Questionnaires \textcolor{red}{were} hosted on Qualtrics and participants \textcolor{red}{accessed} the questionnaires using a laboratory computer.

Participants \textcolor{red}{were} allowed to skip questions they \textcolor{red}{did} not wish to answer. For any one questionnaire, a response rate of less than $75\%$ of questions, or giving the same response for more than $75\%$ of all questions, \textcolor{red}{invalidated} the data from that questionnaire. Participants \textcolor{red}{would be} replaced if they \textcolor{red}{answered} less than $75\%$ of the questions on the conscientiousness scale (the others are exploratory).

@@

The aim of this experiment is to determine if there is a relationship between pre-crastination and the sub-optimal behaviour we observe in the split-half visual search task. Following \cite{nowakowska2017, clarke2019}, each participant's strategy \textcolor{red}{was} represented by the proportion of fixations two-through-five directed to the difficult half of the search area. We \textcolor{red}{used} a Bayesian approach to estimate the extent to which performance in the pre-crastination bucket task is predictive of visual search strategy. Our approach to Bayesian modelling \textcolor{red}{followed} the advice given in \cite{mcelreath2016}, with models fitted using R \cite{r2019} and Stan \cite{carpenter2017stan}.

As our independent variable is a proportion, we fit a model using beta regression \cite{ferrari2004beta} with a logit link for for $\mu$ (mean) and a log link for $\phi$ (precision). We \textcolor{red}{used} conservative priors: $\beta \sim\mathcal{N}(0, 0.50)$ and $\gamma \sim\mathcal{N}(0, 1)$ (where $\beta$ and $\gamma$ are the coefficients for $mu$ and $\gamma$ respectively). This means that we are assuming that the mean of each group is 0.50, with a $95\%$ HPDI $= [0.27, 0.73]$\footnote{For comparison, the mean strategy score for the participants in \cite{nowakowska2017} with $n=14$ is 0.58, with a range of $[0.10, 0.99]$. Similarly, \cite{clarke2019} ($n=57$) found a mean of 0.60 with a range of $[0.06, 0.98]$.}. Our prior for the difference between groups is $\beta \sim\mathcal{N}(0, 0.50)$. We have included pilot data (above) to demonstrate our planned analysis. We have previously used this analysis approach with this paradigm to explore the effect of motivation on visual search strategy \cite{james2019}.

We also \textcolor{red}{measured} the relationship between the personality measures and tendency to pre-crastinate, using similar methods to those outlined above. If our measures of pre-crastination \textcolor{red}{turned} out to be mainly binary \textcolor{red}{which they did}, then we \textcolor{red}{planned to} use Bayesian logistic regression to measure the relationship. Otherwise, we \textcolor{red}{would have reported} an $R^2$ statistic.

\subsection{Outcome-neutral conditions} The ability to test the stated hypotheses depends on replicating both the pre-crastination behaviour and the variability in visual search efficiency observed in previous studies. Our pilot data achieve this replication. Given that we \textcolor{red}{planned} to repeat the same conditions with a larger sample, it \textcolor{red}{as} unlikely that we \textcolor{red}{would} not be able to test our hypotheses. Nonetheless, in our pilot results, the proportion of participants who were categorized as precrastinators (13/30) was smaller than in the most similar previous experiment (Fournier et al., \cite{fournier2019task}, 36/49). Some variation in the proportion can be expected, but a very high ($>90\%$) or very low ($<10\%$) prevalence of pre-crastination \textcolor{red}{would have suggested} there is something in the way we set up or instructed the bucket task that provoked an unrepresentative behaviour in our participants, and \textcolor{red}{would} not be able to use these data to test our hypotheses. It \textcolor{red}{was} also critical that we find inter-participant variability in search strategy. Our pilot data replicate this variation as well, and it \textcolor{red}{was} difficult to imagine why variability would be restricted in our larger sample. Nonetheless, if the variability in our sample \textcolor{red}{had been} less than 0.1 (= half the standard deviation of the pilot data (0.2)), we \textcolor{red}{would not have proceeded} to use these data to test our hypotheses.

@@

The main (pre-registered) hypothesis motivating this experiment is that participants who pre-crastinate will also be sub-optimal (in terms of making more early eye movements to the homogeneous half of the display) in the split-half visual search task. After carrying out our pilot experiment, it \textcolor{red}{looked} like there may be also be a difference in speed-accuracy trade-offs. If this (or any other differences in eye movements) \textcolor{red}{had appeared} to be an interesting effect after we \textcolor{red}{collected} our full dataset, we \textcolor{red}{would have carried} out suitable exploratory analysis. We also \textcolor{red}{investigated} the possibility of further links between the personality measures, pre-crastination and visual search.

>>>>

% \maketitle
\begin{abstract}
How do we decide where to search for a target? Optimal search relies on first considering the relative informational value of different locations, and then executing eye movements to the best options. But many participants consistently move their eyes to locations that can be easily ascertained to neither contain the target, nor to provide new information about the target's location. Here we asked whether this sub-optimal search behaviour represents a specific example of a general tendency towards \textit{pre-crastination: starting sub-goals of a task before they are needed, and in so doing, spending longer doing the task than is necessary. To test this hypothesis, we asked 200 participants to do two tasks: retrieve two heavy buckets (one close and one far), and search for a line segment. Pre-crastination is defined as consistently picking up the closer bucket first, versus the more efficient strategy of picking up the farther bucket first. Search efficiency is the proportion of fixations directed to more cluttered regions of the search array. Based on pilot data, we predicted an association of pre-crastination with inefficient search strategies. Personality inventories were also administered to identify stable characteristics associated with these strategies. In the final dataset, there was no clear association between search strategy and pre-crastination, nor did these correlate strongly with any of the personality measures collected.}
\end{abstract}

@@

\begin{figure}
\centering
\includegraphics[width=6cm]{Figures/split-half.png}
\caption{An example of the split-half line segment stimuli. The target is the unique line segment oriented $45^{\circ}$ to the right. Participants who direct their saccades to the heterogeneous half of the display are faster to correctly respond target absent/present than those who fixate the homogeneous half of the display.}
\label{fig:stimulus}
\end{figure}

@@

In the present study, we investigated the hypothesis that participants who are sub-optimal in our split-half line segment search task have a tendency towards \textit{pre-crastination}, a phenomenon where participants prioritise the completion of a sub-goal, even if it results in extra effort overall \cite{rosenbaum2014}. In the original study, participants were asked to walk down a corridor, pick up one of two heavy buckets as they passed, and carry it to the finish line. The two buckets were placed at different distances between the start and finish line, and the optimal (in terms of minimising effort) strategy is to pick up the bucket that is furthest from the starting position and closer to the finish line. Despite this simple solution, most participants favoured picking up the first bucket they came to, even though that resulted in them having to carry it further. This tendency was named \textit{pre-crastination}, and has since been replicated several times in both humans \cite{fournier2019task} and pigeons \cite{wasserman2015}. In an even more dramatic version of the task, Fournier and colleagues (2019) asked participants to go get two buckets - one close and one further away - and bring them back to set them on a table behind them. The majority (36 out of 49 participants in the key condition) chose to pick up the close bucket first, carry it out to the further bucket, and then bring both back, even though this order is clearly more effortful than picking up the far bucket and then grabbing the close one on the way back to the table.

As a first step to assessing our hypothesis, we conducted a pilot study to ensure we would replicate the variability between participants in a shorter version of the search task, and that we could clearly classify people into two groups based on whether they pick up the close bucket first (i.e. "pre-crastinators") or the farther bucket (optimal). The pilot data were also intended to be used to refine our approach to data processing, visualization, and analysis. Both of the previous findings (search variability, \cite{nowakowska2017}, and pre-crastination, \cite{fournier2019task}) were clearly replicated in the pilot experiment. Surprisingly, the data suggested a relatively robust relationship between pre-crastination and visual search strategy, but in the opposite direction to the one which we originally expected, with pre-crastinators having a tendency to search more efficiently rather than less. We therefore revised our aim to be more data-driven than the original hypothesis, aiming to estimate the variability in search performance accounted for by pre-crastination. The pilot data also suggested that the relationship between pre-crastination and visual search may by mediated by differences in speed-accuracy trade-offs between participants, so we planned to explore this aspect of visual search as well.

If we confirm the existence of a relationship between these two tasks, a natural question is whether this can be accounted for by personality traits of the individuals.  A personality trait is an enduring pattern of thoughts, feelings, and behaviours that is stable across time and contexts \cite{funder2016}. Previous research suggests that those who precrastinate are motivated, responsible, and energetic \cite{rosenbaum2019}. Specifically, \cite{sauerberger2019} found a correlation of $r = 0.22$ between precrastinaion and conscientiousness, which we attempted to replicate. Speculatively, these traits may also cause participants to search in a more thorough, but less efficient, manner, aligning with the interpretation that precrastinating, although costly, may not be irrational to the degree that participants prefer maximizing thoroughness over maximizing efficiency. Personality traits in this study were examined to help further uncover the individual difference factors associated with precrastination and different visual search strategies.

Our experiment tested the hypothesis that pre-crastination might represent a rational approach to doing tasks, i.e., a reasonable tendency to get the difficult part of the task out of the way first. If precrastination had been positively related to efficient search, this would be evidence in favour of a ``rational'' interpretation of precrastination, as opposed to the alternative interpretation that it reflects an irrational impulse to grab the closest task-related object (in which case, a negative correlation with search efficiency would have been more likely). In addition, the experiment had the potential to assess whether the already-established link between pre-crastination and conscientiousness could generalize, and be a potential explanation for the wide range of different search strategies previously observed. This would have important implications for theories of visual search, which tend to make assumptions about how ''people'' (as a group) direct their eyes during search; if personality traits can be directly predictive of eye movement strategies, this would challenge the field to more carefully refine its assumptions. In addition to the clear theoretical contribution our results could have had, they could also have illustrated a case where efficient/optimal tendencies in one circumstance can translate to inefficient choices in others. Finally, we have noticed in many fields that there is a lack of correlational studies relating behavioural measures to each other (as opposed to relating behavioural measures to personality traits).

@@

As such, we investigated the following hypotheses:

@@

We planned to recruit 200 participants for this experiment. This large sample size is due to the addition of personality measures: Larger samples provide greater power to detect the typical effect sizes in those fields, reduce Type I error, and increase the chances of replicable findings \cite{fraley2014}. Participants were recruited via participant panels and opportunity sampling at the universities of Aberdeen and Essex. The protocol was approved by the ethics committees at both universities. Participants completed the bucket-retrieval task both before and after the visual search task, so no counterbalancing was needed. Additional participants were recruited to replace those excluded from data analysis (details below).

@@

Figure \ref{fig:buckets} is a photograph of the bucket task set-up. Two 10 litre buckets were filled with sand until the total weight of each bucket was 3kg. The experiment took place in a quiet corridor. Buckets were placed at 6ft and 16ft away from the start position, which was marked as a T with green tape. Buckets were placed on crates at about hand height. Just behind the start position was a pair of crates on which to set the buckets down to end the trial.

@@

The task replicates that used in \cite{fournier2019task}, in which participants were instructed to pick up two buckets and place them on the crates behind the start position. We closely followed the methods and instructions as described in their appendix. Each participant completed three trials before the visual search task, and three trials after. While the experimenter was setting up the buckets for the next trial, the participant was asked to walk over to a nearby window and look outside until asked to return. The full protocol and instructions given to participants is available at https://osf.io/5aq4c/.

@@

Participants were classified as "pre-crastinators" if they picked up the closer bucket first, and "optimal" if they picked up the far bucket first. Based on the pilot data, and that of \cite{fournier2019task}, we expected the results from the bucket task to be largely binary, with participants picking up either the close or the far bucket on every trial. Our plan was the following: If the data are similarly binary in this experiment, we will continue to treat pre-crastination as a two-level categorical factor. Participants who pick up the closest bucket on at least five of the six trials will be classed as pre-crastinators, while those who pick up the closest bucket on no more than two out of six trials will be non-pre-crastinators. Participants with intermediate behaviour will be excluded.

There was also a chance that, unlike \cite{fournier2019task}, our sample of participants would give rise to a larger range of intermediate behaviours. If more than $25\%$ of our participants would have been excluded under the coding scheme outlined above, then we would have treated our pre-crastination measure as a three-level factor (if a clear classification is apparent). In this case, the same Bayesian beta regression model would have been fit to the data.

@@

Stimuli were presented on a 17 inch CRT monitor with a resolution of $1024 \times 768$. Stimulus generation, presentation and data collection were controlled by Matlab and psychophysics toolbox \cite{brainard1997,cornelissen2002} run on a mac pro computer. The position of the right eye was recorded using a desktop-mounted EyeLink 1000 eye tracker (SR Research, Canada) sampling eye position at 1000Hz.

We used the same arrays of line segments as in \cite{nowakowska2017} (see Figure \ref{fig:stimulus}). These arrays consist of 22 column and 16 rows on a uniform grey background. The target line is always tilted $45^{\circ}$ degrees to the right, while the mean distractor angle is perpendicular at $45^{\circ}$ degrees to the left. Search difficulty was manipulated by sampling from either a narrow $30^{\circ}$ range of distractor line orientations (homogeneous) or a wide $106^{\circ}$ range (heterogeneous). Half of each search array consists of homogeneous line segments, while the other half is heterogeneous. Which side is heterogeneous was randomly determined on each trial. We used 96 search trials in total, half of which contained a target. This number of trials was selected based on simulating the results of shorter experiments using the data from \cite{nowakowska2017} (see Figure \ref{fig:num_trials}). The target could be located in any of the possible locations apart from the middle four vertical columns.

@@

\subsubsection{Procedure} Before the start of the visual search experiment, participants undergo a nine-point calibration sequence. Following this, participants were instructed to report, as quickly as possible, whether a line tilted $45^{\circ}$ to the right was present or not, using the up (present) or down (absent) arrow key. Each search trial begins with a black fixation point (letter \texttt{x}) subtending $1.5\times 2.5$cm ($1.9^{\circ}\times 3.1^{\circ}$), presented at the centre of the computer screen. On the press of a space bar, the stimulus is displayed until the participant makes a response (or times out after 60 seconds). Auditory feedback in the form of a beep, and a 2s red screen, immediately follows incorrect key presses. A set of 8 practice trials precedes the experimental trials.

@@

Data from participants who fail to achieve at least $75\%$ accuracy for \textit{easy} and \textit{absent} conditions were excluded as it suggests that they did not understand the task. Fixations during trials were classified as falling on the homogeneous or heterogeneous half of the display, with fixations falling within the central four columns of line segments being excluded. Following \cite{nowakowska2017} we summarised each participant's strategy as the proportion of fixations two through five falling on the heterogeneous side of the display during target absent trials. Trials with fewer than five fixations were excluded, and we only analysed data from participants who have at least 10 trials.

@@

We administered three personality questionnaires. The first questionnaire is the second iteration of the Big Five Inventory (BFI-2 \cite{soto2017}). The BFI-2 measures five broad personality traits: extraversion (e.g., ``is outgoing, sociable''), agreeableness (e.g., ``has a forgiving nature''), conscientiousness (e.g., ``is efficient, gets things done''), negative emotionality (e.g., ``can be tense''), and open-mindedness (e.g., ``is fascinated by art, music, or literature''). Based on previous research, we suspected that precrastination will have the strongest relationship with conscientiousness. Those who are high in conscientiousness are organised, productive, and responsible, and may have an urge to pick up a bucket as soon as possible.

The second personality questionnaire is the Barratt Impulsiveness Scale (BIS-11 \cite{patton1995}). The BIS-11 measures overall impulsiveness, as well as three subtypes: attentional impulsiveness (``I don't `pay attention'''), motor impulsiveness (``I act on the spur of the moment''), and non-planning impulsiveness (``I say things without thinking''). Based on previous research, we suspected that neither impulsiveness nor its subscales will be related to precrastination.

@@

Personality questionnaires were administered to participants at the end of the experiment to prevent them from influencing the behavioural measures. Questionnaires were hosted on Qualtrics and participants accessed the questionnaires using a laboratory computer.

Participants were allowed to skip questions they did not wish to answer. For any one questionnaire, a response rate of less than $75\%$ of questions, or giving the same response for more than $75\%$ of all questions, invalidated the data from that questionnaire. Participants would be replaced if they answered less than $75\%$ of the questions on the conscientiousness scale (the others are exploratory).

@@

The aim of this experiment is to determine if there is a relationship between pre-crastination and the sub-optimal behaviour we observe in the split-half visual search task. Following \cite{nowakowska2017, clarke2019}, each participant's strategy was represented by the proportion of fixations two-through-five directed to the difficult half of the search area. We used a Bayesian approach to estimate the extent to which performance in the pre-crastination bucket task is predictive of visual search strategy. Our approach to Bayesian modelling followed the advice given in \cite{mcelreath2016}, with models fitted using R \cite{r2019} and Stan \cite{carpenter2017stan}.

As our independent variable is a proportion, we fit a model using beta regression \cite{ferrari2004beta} with a logit link for for $\mu$ (mean) and a log link for $\phi$ (precision). We used conservative priors: $\beta \sim\mathcal{N(0, 0.50)}$ and $\gamma \sim\mathcal{N}(0, 1)$ (where $\beta$ and $\gamma$ are the coefficients for $mu$ and $\gamma$ respectively). This means that we are assuming that the mean of each group is 0.50, with a $95\%$ HPDI $= [0.27, 0.73]$\footnote{For comparison, the mean strategy score for the participants in \cite{nowakowska2017} with $n=14$ is 0.58, with a range of $[0.10, 0.99]$. Similarly, \cite{clarke2019} ($n=57$) found a mean of 0.60 with a range of $[0.06, 0.98]$.}. Our prior for the difference between groups is $\beta \sim\mathcal{N}(0, 0.50)$. We have included pilot data (above) to demonstrate our planned analysis. We have previously used this analysis approach with this paradigm to explore the effect of motivation on visual search strategy \cite{james2019}.

We also measured the relationship between the personality measures and tendency to pre-crastinate, using similar methods to those outlined above. If our measures of pre-crastination turned out to be mainly binary which they did, then we planned to use Bayesian logistic regression to measure the relationship. Otherwise, we would have reported an $R^2$ statistic.

\subsection{Outcome-neutral conditions} The ability to test the stated hypotheses depends on replicating both the pre-crastination behaviour and the variability in visual search efficiency observed in previous studies. Our pilot data achieve this replication. Given that we planned to repeat the same conditions with a larger sample, it as unlikely that we would not be able to test our hypotheses. Nonetheless, in our pilot results, the proportion of participants who were categorized as precrastinators (13/30) was smaller than in the most similar previous experiment (Fournier et al., \cite{fournier2019task}, 36/49). Some variation in the proportion can be expected, but a very high ($>90\%$) or very low ($<10\%$) prevalence of pre-crastination would have suggested there is something in the way we set up or instructed the bucket task that provoked an unrepresentative behaviour in our participants, and would not be able to use these data to test our hypotheses. It was also critical that we find inter-participant variability in search strategy. Our pilot data replicate this variation as well, and it was difficult to imagine why variability would be restricted in our larger sample. Nonetheless, if the variability in our sample had been less than 0.1 (= half the standard deviation of the pilot data (0.2)), we would not have proceeded to use these data to test our hypotheses.

@@

The main (pre-registered) hypothesis motivating this experiment is that participants who pre-crastinate will also be sub-optimal (in terms of making more early eye movements to the homogeneous half of the display) in the split-half visual search task. After carrying out our pilot experiment, it looked like there may be also be a difference in speed-accuracy trade-offs. If this (or any other differences in eye movements) had appeared to be an interesting effect after we collected our full dataset, we would have carried out suitable exploratory analysis. We also investigated the possibility of further links between the personality measures, pre-crastination and visual search.
